%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications
\linespread{1.2}

%------------
%\usepackage{enumitem}
%\renewenvironment{entrylist}{
%  \begin{itemize}[leftmargin=0.9in]
%}{
%  \end{itemize}
%}
%\renewcommand{\bfseries}{\headingfont\color{headercolor}}
%\renewcommand{\entry}[4]{
%  \item[#1]
%    \textbf{#2}
%    \hfill
%    {\footnotesize\addfontfeature{Color=lightgray} #3}\\%
%    #4\vspace{\parsep}
%}
%-------
\begin{document}

\header{陆}{哲琪}{实习生} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{个人信息}
性别男, 24周岁
出生地: 浙江舟山
\section{联系方式}
% Zijinggang Campus
浙江省杭州市
浙江大学紫金港校区
蒙民伟楼306-1
~
+86-17816861269
albuscrow@gmail.com
\section{外语}
English CET4
\section{编程语言}
熟练掌握: Java, C/C++
基本掌握: Python, C\# JS/HTML/CSS, SQL
大致了解: Lisp, Haskell
%{\color{red} $\varheartsuit$} Java 熟练掌握
\section{技术关键字}
{\color{red} $\varheartsuit$} Android,Linux
Git, Cmake
Vim/Emacs, Latex
OpenGL, GLSL
SSH, Django
\section{兴趣}
折腾各种系统和软件
学习新的语言和框架
看书,\quad跑步,\quad玩游戏
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}
\begin{entrylist}

%------------------------------------------------

\entry
{09/14--Now}
{Masters {\normalfont of Computer Technology}}
{Zhejiang University}
{Specialization in Computer Graphics. Now researching on accurate free-form deform(AFFD).}

%------------------------------------------------

\entry
{09/10--06/14}
{Bachelor {\normalfont of Computer Science and Technology}}
{Chongqing University}
{ Detailed achievements:
    \begin{itemize}
    \item Master solid fundamental and professional knowledge of computer.
    \item Won many scholarships like Nation Scholarship and so on.
    \item Lead the team to participate in the American Mathematical Modeling Contest and won Finalist Award.
    \item Got recommended postgraduate qualification to Zhejiang University with excellent grades.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------

\entry
{07/15--Now}
{Dihansi Tech Co., Ltd.}
{Hangzhou, China}
{\emph{Android Application} \\
    I developed two Android apps(i-ez and D-control) which are used to control Smart Home for the company.
I learned much about communication with socket.\\
Detailed skill used:
\begin{itemize}
    \item Communication via Socket(TCP/UDP)
    \item Transmission data via http
    \item Build by gradle
    \item Collaborative Development with git
    \item Android development technology
\end{itemize}}

\entry
{08/14--11/14}
{Huajian Tech Co., Ltd.}
{Hangzhou, China}
{\emph{Android Application} \\
    The company is a outsourcing company,I developed three Android apps for them:
\begin{itemize}
    \item HuiXiaoMi, a meeting scheduling management software whose party A is a known office software company.
    \item IT-Management, an IT asset management software which is used for the management of computer, rooter and so on.
    \item D-fire, an E-commerce management software which is used by seller who can add/modify/delete/query goods via the app.
\end{itemize}}

\entry
{08/12--07/13}
{NineTon Tech Co., Ltd.}
{Chongqing, China}
{\emph{Web app \& Android Application} \\
    My friends set up the start-up company which I contribute my technology to beconme a sharehloder.
    In the company I developed two software:
    \begin{itemize}
        \item 365-shimingzhi, a food and beverage platform like Public Remark Web which include an Android client and a web app. This product is developed with others.It's also my first experience develop something in real world.
        \item Guoguo Candy, An Android app which can buy snacks from taobao.  It's my first experience develop a softwart all by myself.
    \end{itemize}}

%------------------------------------------------

\end{entrylist}

\end{document}
